---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hw4)
library(plyr)
```

To use the function `mylm`, use the build in dataset "mtcars" as an example.

```{r}
mylm(mpg~cyl+disp, data = mtcars)
lm(mpg~cyl+disp, data = mtcars)
```

MORE SPECIFIC WAY TO USE `mylm`:
Estimated coefficients:
* use ordinary least square estimation:
```{r}
mylm(mpg~cyl+disp+wt+qsec, data = mtcars)
lm(mpg~cyl+disp+wt+qsec, data = mtcars)
```

* penalty on including more variable, which supports model selection
```{r}
mylm(mpg~cyl+disp+wt+qsec, data = mtcars, penalty = 10)
```

* deal with sparse regression by doing estimation using coordinate descent.
```{r}
mtcars_modified <- mtcars[1:3,]
mylm(mpg~cyl+disp+wt+qsec, data = mtcars_modified, useSparse = TRUE)
```

* deal with sparse regression and set penalty on larger modle
```{r}
mylm(mpg~cyl+disp+wt+qsec, data = mtcars_modified, useSparse = TRUE, penalty = 20)
```

* want faster calculation using rcpp to approximate estimation.
```{r}
mylm(mpg~cyl+disp+wt+qsec, data = mtcars_modified, useSparse = TRUE, useCpp = TRUE)
```



