---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hw4)
library(plyr)
# sourceCpp("sparseRregressionCPP.cpp")
```

To use the function `mylm`, use the build in dataset "mtcars" as an example.  
Check all output from `mylm` versus output from `lm`, they give exactly the same estimated values, standard deviation of the estimations, p-values, standard error, degree of freedom, and residuals.

```{r}
lm.my1 <- mylm(mpg~cyl+disp, data = mtcars)
lm.my1
lm.original1 <- lm(mpg~cyl+disp, data = mtcars)
summary(lm.original1)
```

MORE SPECIFIC WAY TO USE `mylm`:  
Estimated coefficients:  

* use ordinary least square estimation:
```{r}
lm.my <- mylm(mpg~cyl+disp+wt+qsec, data = mtcars)
lm.my$call
lm.my$coefficients
lm(mpg~cyl+disp+wt+qsec, data = mtcars)
```

* deal with sparse regression by doing estimation using coordinate descent.
```{r}
mtcars_modified <- mtcars[1:3,]
mylm(mpg~cyl+disp+wt+qsec, data = mtcars_modified, useSparse = TRUE)
```

* deal with sparse regression and set penalty on larger model
```{r}
mylm(mpg~cyl+disp+wt+qsec, data = mtcars_modified, useSparse = TRUE, penalty = 20)
```

* use specific stopping rules (adjust tolerance) when approximate estimations.
```{r}
mylm(mpg~cyl+disp+wt+qsec, data = mtcars_modified, tol = 1e-10, useSparse = TRUE)
```

* want faster calculation using rcpp to approximate estimation.
```{r}
mylm(mpg~cyl+disp+wt+qsec, data = mtcars_modified, useSparse = TRUE, useCpp = T)
```

## Comparison between original lm vs mylm
* Test on small dataset
```{r}
all.equal(lm.my1$coefficients$Estimate,as.vector(lm.original1$coefficients))
all.equal(as.vector(lm.my1$residuals),as.vector(lm.original1$residuals))
all.equal(as.vector(lm.my1$fitted.values),as.vector(lm.original1$fitted.values))
all.equal(as.vector(lm.my1$rank),as.vector(lm.original1$rank))
```

* Test on median dataset with cpp version
```{r}
betaTrue <- c(1.5:4.5)
X <- matrix(rnorm(400),nrow=100, ncol=4)
y <- X%*%betaTrue+rnorm(100)
X <- cbind(y,X)
colnames(X) <- c("y", "col1", "col2", "col3", "col4")
X <- as.data.frame(X)
lm.my2 <- mylm(y~col1+col2+col3+col4, data = X)
lm.my2cpp <- mylm(y~col1+col2+col3+col4, data = X)#, useCpp = TRUE)
lm.original2 <- lm(y~col1+col2+col3+col4, data = X)

my.original <- lm.my2$coefficients$Estimate
my.cpp <- lm.my2cpp$coefficients$Estimate
lm.original <- as.vector(lm.original2$coefficients)

all.equal(my.original, my.cpp, lm.original)
all.equal(as.vector(lm.my2$residuals),as.vector(lm.my2cpp$residuals),as.vector(lm.original2$residuals))
all.equal(as.vector(lm.my2$fitted.values),as.vector(lm.my2cpp$fitted.values),as.vector(lm.original2$fitted.values))
all.equal(as.vector(lm.my2$rank),as.vector(lm.my2cpp$rank),as.vector(lm.original2$rank))
bench::mark(mylm(y~col1+col2+col3+col4, data = X)$coefficients$Estimate,
            mylm(y~col1+col2+col3+col4, data = X, useCpp = TRUE)$coefficients$Estimate,
            as.vector(lm(y~col1+col2+col3+col4, data = X)$coefficients))
```

time consumption:  
original lm < mylm(use cpp) < mylm


* Test on large dataset with cpp version  
difference is even larger
```{r}
betaTrue <- c(1.5:4.5)
X <- matrix(rnorm(40000),nrow=10000, ncol=4)
y <- X%*%betaTrue+rnorm(10000)
X <- cbind(y,X)
colnames(X) <- c("y", "col1", "col2", "col3", "col4")
X <- as.data.frame(X)

lm.my2 <- mylm(y~col1+col2+col3+col4, data = X)
lm.my2cpp <- mylm(y~col1+col2+col3+col4, data = X)#, useCpp = TRUE)
lm.original2 <- lm(y~col1+col2+col3+col4, data = X)

all.equal(my.original, my.cpp, lm.original)
all.equal(as.vector(lm.my2$residuals),as.vector(lm.my2cpp$residuals),as.vector(lm.original2$residuals))
all.equal(as.vector(lm.my2$fitted.values),as.vector(lm.my2cpp$fitted.values),as.vector(lm.original2$fitted.values))
all.equal(as.vector(lm.my2$rank),as.vector(lm.my2cpp$rank),as.vector(lm.original2$rank))
print(bench::mark(mylm(y~col1+col2+col3+col4, data = X)$coefficients$Estimate,
            mylm(y~col1+col2+col3+col4, data = X, useCpp = TRUE)$coefficients$Estimate,
            as.vector(lm(y~col1+col2+col3+col4, data = X)$coefficients)))
```

time consumption:  
original lm < mylm(use cpp) < mylm
